---
title: "Data 607 - Week 12 Assignment"
author: "Joseph E. Garcia"
date: "November 19, 2018"
output: html_document
---
```{r}
library(odbc)
library(dplyr)
library(dbplyr)

```

## We pulling the data down from mySQL:
```{r}
db <- DBI::dbConnect(odbc::odbc(), "SQL")
```

```{r}
movie <- as.data.frame(db %>% tbl("movie"))
movie
```


```{r}
rating <- as.data.frame(db %>% tbl("rating"))
rating
```


```{r}
merge(movie,rating, by = c('movie_id'), all.x=TRUE)

```


Loading Data Into MongoDB

##Now to load the data into a MongoDB. First we need a connection:
```{r}
library(mongolite)
mdb_movie = mongo(collection = "movie", db = "movie")
```

```{r}
library(mongolite)
mdb_rating = mongo(collection = "rating", db = "rating")
```


##Now we can load the collection name movie into the MongoDB.
```{r}
mdb_movie$insert(movie)
```


```{r}
mdb_rating$insert(rating)
```

## Now we run a print out of the database to make sure the data was uploaded.
```{r}
alldata_movie <- mdb_movie$find('{}')
head(alldata_movie)
```


```{r}
alldata_rating <- mdb_rating$find('{}')
head(alldata_rating)
```

```{r}

merge(head(alldata_movie),head(alldata_rating), by = c('movie_id'), all=TRUE)
```

######The migration from MySQL to MongoDB is complete.


##Advantages and Disadvantages of storing the data in a relational database vs. your NoSQL database.


######Advantages of using a relational database: is that you can reduce data integrity and eliminate a lot of anomolies.

######Disadvantages of NoSQL:store is easier to retrieve and the data access is faster as the data but need to consider YOUR use case more clearly before you commit to much to a system.

