---
title: "Data 607 - Week 5 Assignment"
author: "Joseph E. Garcia"
date: "September 25, 2018"
output: html_document
---

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(plotly)
```

```{r}

airlinesdata<-read.csv("Data607-Week5 Assignment.csv",header=TRUE,sep=",")

head(airlinesdata)
```

```{r}
selectdata<-airlinesdata %>%  
  filter(!is.na(Phoenix)) %>% 
    rename("Los Angeles"=Los.Angeles,"San Diego"=San.Diego,"San Francisco"=San.Francisco)

selectdata$Airlines<-as.character(selectdata$Airlines)
selectdata$Airlines[selectdata$Airlines==""]<-c("ALASKA","AM WEST")

selectdata
```

```{r}

```{r}
tidydata<-selectdata %>% 
  gather(key=Cities,value=Number,3:7)
tidydata<-arrange(tidydata,Airlines,Arrival)
head(tidydata)
```

```{r}
tidydata %>% 
  group_by(Airlines,Arrival) %>% 
  summarize(Total=sum(Number))
```

```{r}
tidydata %>% 
  group_by(Airlines) %>% 
  summarize(Total=sum(Number))
```




```{r}
ggplotly(ggplot(filter(tidydata,Arrival=="Delayed"),aes(Cities,Number,color=Airlines))+geom_point(size=5)+ggtitle("Delayed Flights")+ylab("Number of Delayed"))
```

```{r}
spreadata<-tidydata %>% 
  spread(Arrival,Number) %>% 
  mutate(Total=Delayed+`On time`,prop=Delayed/Total)
```



```{r}
ggplotly(ggplot(spreadata,aes(x=Cities,y=prop))+geom_bar(aes(fill=Airlines),stat="identity",position="dodge", colour="#D55E00")+ylab("Proportion of Delayed")+ggtitle("Delayed Flights"))
```

